Gravitational Lens Modelling in a Citizen Science Context

### 2014-10-01 text/ms.tex
edits following comments from AM

The \sw sims are described in detail in More et al (in prep), but
relevant here is that the sims were of three kinds, as follows.
\begin{enumerate}
\item Lensed quasars: The lens is modelled as a singular isothermal
  ellipsoid (SIE) and a constant external shear whereas the quasar is
  represented with a circular Gaussian source whose size is given by
  the point spread function (PSF) in each imaging band.
\item Galaxy-scale lenses: The lens model is the same as above whereas
  the background galaxy is modelled as an elliptical de~Vaucouleurs.
\item Groups-scale lenses: The lens model includes SIE models for the
  central galaxy and the inner group members, plus a circular NFW
  (ref) to represent the underlying dark matter distribution and the
  background galaxy model stays the same as galaxy-scale lenses.
\end{enumerate}
The {\tt gravlens} program \citep{2001astro.ph..2340K} was used.
Formulas for the lenses appear in \cite{2001astro.ph..2341K}. The SIE
lenses follow equations (33--35) of that work, with core radius set to
zero.  The NFW lens is in equations (48) and (50), while shear is the
$\gamma$ term in equation (76).

>>>>

The \sw sims are described in detail in More et al (in prep), but
relevant here is that the sims were of three kinds, as follows.
\begin{enumerate}
\item Lensed quasars: The lens is modelled as a singular isothermal
  ellipsoid (SIE) and a constant external shear whereas the quasar is
  represented with a circular Gaussian source whose size is given by
  the point spread function (PSF) in each imaging band.
\item Galaxy-scale lenses: The lens model is the same as above whereas
  the background galaxy is modelled as an elliptical de~Vaucouleurs.
\item Group-scale lenses: The lens model includes SIE models for the
  central galaxy and the inner group members, plus a circular NFW
  \citep{1996ApJ...462..563N,1997ApJ...490..493N} to represent the
  underlying dark matter distribution and the background galaxy model
  stays the same as galaxy-scale lenses.
\end{enumerate}
The {\tt gravlens} program \citep{2001astro.ph..2340K} was used.
Formulas for the lenses appear in \cite{2001astro.ph..2341K}. The SIE
lenses follow equations (33--35) of that work, with core radius set to
zero.  The NFW lens is in equations (48) and (50), while shear is the
$\gamma$ term in equation (76).
